---
title: "Final Data Science Project Code"
author: "Joe Patrick"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import all necessary libraries 

```{r}
library(rvest)
library(tidyverse)
sessionInfo()
```

# Create functions

### 1. Import and clean Wiki data

This function downloads the url and cleans it by removing citations, lowering case, and trimming white space. 

```{r}
input_data <- function(x) {
  x <- read_html(x) %>% 
    html_elements("#collapsibleTable1 tr:nth-child(2) td , .tright+ ul li , .infobox small , #mw-content-text p") %>% 
    html_text() %>% 
    str_remove_all("\\[\\d+?\\]") %>%
    str_trim() %>% 
    tolower()
  
}
```

### 2. Check for 'mnogo' vs. 'puno'

This function processes the object to see if any version of puno/mnogo are present. 

```{r}
mnogopuno <- function(x) {
  str_extract_all(x, "(mnogo|puno|много|пуно) \\b") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```

### 3. Check for [-isa] vs. [-ira|-ova]

This function tests for clusters of -isa (HR intl verbs) or -ira, -ova (SR intl verbs). It does return false positives though, because this is a common syllable pattern. 

```{r}
isa_iraova <- function(x) {
  str_extract_all(x, "\\w+ [a-z\\p{Cyrillic}]+(isa|ira|ova|иса|ира|ова) \\b") %>%
    keep(~length(.x)>0)%>%
    flatten_chr()
}
```

### 4. Check for 'ko' vs. 'tko'

This function tests for presence of ko/tko and their variants (in trigrams). It does return false positives though, because this is a common syllable pattern. 

```{r}
ko_tko <- function(x) {
  str_extract_all(x, "\\b [a-z\\p{Cyrillic}]+(ko|tko|ко|тко) \\b") %>%
    keep(~length(.x)>0)%>%
    flatten_chr()
}
```

### 5. Check for Da vs. Infinitive construction

Finds 'da' and preceding and following word.
Primary feature: da + finite verb (SR) vs. infinitive (HR)-- da posluzi vs posluziti

```{r}
da_inf <- function(x) {
  str_extract_all(x, "(((\\w+ da \\w+)|(\\w+ да \\w+))|(\b ([a-z\\p{Cyrillic}]+(iti|ити) \\w+)))")%>%
    keep(~length(.x)>0)%>%
    flatten_chr()
}
```

### 6. Check for 's' vs. 'sa'

Finds use of preposition 's' (HR)(4x more frequent in HR) or 'sa' (SR)(2.5x more freq in SR)(Tosovic 2009)

```{r}
sorsa <- function(x) {
  str_extract_all(x, "(\\w+ s \\w+ | \\w+ sa \\w+)|(\\w+ с \\w+ | \\w+ са \\w+) ") %>%
    keep(~length(.x)>0)%>%
    flatten_chr()
}
```

### 7. Check for 'Što' vs. 'Šta'

Finds use of 'Što' (SR) vs. 'Šta'(HR)

```{r}
stosta <- function(x, ...) {
  str_extract_all(x, "(što|šta|што|шта) \\b") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```


### 8. Check for 'Da li' vs. 'Je li'

Finds da li (SR) vs. je li (HR)- for yes/no questions and other limited syntactic constructions. 
```{r}
dali_jeli <- function(x) {
  str_extract_all(x, "\\b(da.li|je.li|да.ли|је.ли)\\b") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```

### 9. Check for Synth future vs. Nonsynth future

Finds use of Synth future (RS) vs. Nonsynth future (HR) constructions.

```{r}
synth_non <- function(x) {
  str_extract_all(x, "(\\b (ću|ćeš|će|ćemo|ćete|ћу|ћеш|ће|ћемо|ћете)\\b)|(\\w*(ću|ćeš|će|ćemo|ćete|ћу|ћеш|ће|ћемо|ћете)\\b)") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```

### 10. Check for 'Treba' variation

Finds use of conjugated Trebam/o/ala (SR)/ impersonal 3rd person Treba (HR)
```{r}
treba <- function(x) {
  str_extract_all(x, "((\\btreba(m|s|mo|te|ju)\\b|\\btreba(?! da))|(\\btreba da\\b))|((\\bтреба(м|с|мо|те|ју)\\b|\\bтреба(?! да))|(\\bтреба да\\b))") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```

### 11. Check for [-rica] vs. [-rka]

Finds use of rica (SR)/ rka (RS), which are suffixes for feminine agent nouns

```{r}
rica_rka <- function(x) {
  str_extract_all(x, "\\w*(rica|rka|риса|рка)\\b") %>% keep(~length(.x)>0) %>%
    flatten_chr()
}
```

# Processing my own data

```{r}
get_feat_df <- function(URL, featFunc) {
  ##Check that both arguments are length 1
  if (length(URL)!= 1 || !is.character(URL)) {
    stop("URL must be a length-1 character vector")
  }
  if (length(featFunc)!= 1 || !is.function(featFunc)) {
    stop("featFunc must be a single function")
  }
  
  ##Get text nodes
  txt <- input_data(URL)
  
  ##Get vector of hits
  featData <- featFunc(txt)
  
  ##Get function name (https://stackoverflow.com/a/10520832)
  funcName <- deparse(substitute(featFunc))
  
  ##Return as dataframe
  tibble(URL, featData) %>% 
    set_names(c("URL", funcName))
}

c("https://sr.wikipedia.org/wiki/%D0%9A%D0%BE%D1%81%D0%BE%D0%B2%D0%BE", "https://sr.wikipedia.org/wiki/%D0%A7%D0%B5%D1%82%D0%BD%D0%B8%D1%86%D0%B8", "https://sr.wikipedia.org/wiki/%D0%A3%D1%81%D1%82%D0%B0%D1%88%D0%B5", "https://sr.wikipedia.org/wiki/%D0%9F%D1%80%D0%B0%D0%B2%D0%BE%D1%81%D0%BB%D0%B0%D0%B2%D0%BD%D0%B0_%D1%86%D1%80%D0%BA%D0%B2%D0%B0_%D1%83_%D0%A6%D1%80%D0%BD%D0%BE%D1%98_%D0%93%D0%BE%D1%80%D0%B8", "https://sr.wikipedia.org/wiki/%D0%9D%D0%B0%D1%86%D0%B8%D0%BE%D0%BD%D0%B0%D0%BB%D0%B8%D0%B7%D0%B0%D0%BC") %>% 
  map_dfr(get_feat_df, da_inf) %>% 
  write_csv("/Users/Joe1/Desktop/DSPROJECT/srdainfa.csv")
```


# Link Bank 

Croatian (HR) and Serbian (SR) wiki links with parentheses and quotes for easy copy-paste:

HR:("https://hr.wikipedia.org/wiki/Kosovo","https://hr.wikipedia.org/wiki/%C4%8Cetnici", "https://hr.wikipedia.org/wiki/Usta%C5%A1e", "https://hr.wikipedia.org/wiki/Pravoslavna_crkva_u_Crnoj_Gori","https://hr.wikipedia.org/wiki/Nacionalizam")

SR:("https://sr.wikipedia.org/wiki/%D0%9A%D0%BE%D1%81%D0%BE%D0%B2%D0%BE", "https://sr.wikipedia.org/wiki/%D0%A7%D0%B5%D1%82%D0%BD%D0%B8%D1%86%D0%B8", "https://sr.wikipedia.org/wiki/%D0%A3%D1%81%D1%82%D0%B0%D1%88%D0%B5", "https://sr.wikipedia.org/wiki/%D0%9F%D1%80%D0%B0%D0%B2%D0%BE%D1%81%D0%BB%D0%B0%D0%B2%D0%BD%D0%B0_%D1%86%D1%80%D0%BA%D0%B2%D0%B0_%D1%83_%D0%A6%D1%80%D0%BD%D0%BE%D1%98_%D0%93%D0%BE%D1%80%D0%B8", "https://sr.wikipedia.org/wiki/%D0%9D%D0%B0%D1%86%D0%B8%D0%BE%D0%BD%D0%B0%D0%BB%D0%B8%D0%B7%D0%B0%D0%BC")